Manuscript

### 2018-12-03 manuscript.Rmd
update rmd

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ccle_ge_summ) <= 1) {
    ccle_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
    ccle_ge_res <-  NA
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
    ccle_ge_res <- paste0("t(", round(ccle_ge_ttest$parameter, 1), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ccle_cn_summ) <= 1) {
    ccle_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
    ccle_cn_res <-  NA
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
    ccle_cn_res <- paste0("t(", round(ccle_cn_ttest$parameter, 1), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
  }
  print("CCLE testing: DONE")

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ctrp_ge_summ) <= 1) {
    ctrp_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_ge_res <-  NA
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
    ctrp_ge_res <- paste0("t(", round(ctrp_ge_ttest$parameter, 1), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ctrp_cn_summ) <= 1) {
    ctrp_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_cn_res <-  NA
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
    ctrp_cn_res <- paste0("t(", round(ctrp_cn_ttest$parameter, 1), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
  }
  print("CTRP testing: DONE")

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_gdsc_ge_summ) <= 1) {
    gdsc_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_ge_res <-  NA
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
    gdsc_ge_res <- paste0("t(", round(gdsc_ge_ttest$parameter, 1), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_gdsc_cn_summ) <= 1) {
    gdsc_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_cn_res <-  NA
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
    gdsc_cn_res <- paste0("t(", round(gdsc_cn_ttest$parameter, 1), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
  }
  print("GDSC testing: DONE")

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(round(ccle_ge_ttest$parameter, 3), round(ctrp_ge_ttest$parameter, 3), round(gdsc_ge_ttest$parameter, 3)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(round(ccle_cn_ttest$parameter, 3), round(ctrp_cn_ttest$parameter, 3), round(gdsc_cn_ttest$parameter, 3)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

@@

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_NOV_27.csv", sep = "\t", header = TRUE)
colnames(g2p)[colnames(g2p) == "Phenotype.ID"] <- "grouped_general_doid"
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)

@@

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

@@

gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", round(gdsc_p_ttest$p.value, 2))

@@

# ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
```

@@

Mutation status summary stats:
```{r}
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
g2p_druggene_all_summ_stats$n_true <- TRUE
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05))
```

Pearson summary stats:
```{r fig.height=4, fig.width=5}
g2p_druggene_pearson_stats <- g2p_druggene_pearson
g2p_druggene_pearson_stats$n_true <- TRUE
g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05))

>>>>

  use_data_ccle <- filter(use_data, Dataset == "CCLE")
  use_data_ccle_ge_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ccle_cn_summ <- use_data_ccle[!is.na(use_data_ccle$Pearson_CN_Abs),] %>% count(InG2P)
  ccle_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ccle_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ccle_ge_summ) <= 1) {
    ccle_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn < 2) {
    ccle_ge_res <-  NA
  }
  else if(use_data_ccle_ge_summ[use_data_ccle_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_ge_ttest <- t.test(use_data_ccle$Pearson_GE_Abs ~ use_data_ccle$InG2P)
    ccle_ge_res <- paste0("t(", trunc(ccle_ge_ttest$parameter), ") = ", round(ccle_ge_ttest$statistic, 2), ", p = ", round(ccle_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ccle_cn_summ) <= 1) {
    ccle_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn < 2) {
    ccle_cn_res <-  NA
  }
  else if(use_data_ccle_cn_summ[use_data_ccle_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ccle_cn_ttest <- t.test(use_data_ccle$Pearson_CN_Abs ~ use_data_ccle$InG2P)
    ccle_cn_res <- paste0("t(", trunc(ccle_cn_ttest$parameter), ") = ", round(ccle_cn_ttest$statistic, 2), ", p = ", round(ccle_cn_ttest$p.value, 3))
  }
  print("CCLE testing: DONE")

  use_data_ctrp <- filter(use_data, Dataset == "CTRP")
  use_data_ctrp_ge_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_ctrp_cn_summ <- use_data_ctrp[!is.na(use_data_ctrp$Pearson_CN_Abs),] %>% count(InG2P)
  ctrp_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  ctrp_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_ctrp_ge_summ) <= 1) {
    ctrp_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_ge_res <-  NA
  }
  else if(use_data_ctrp_ge_summ[use_data_ctrp_ge_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_ge_ttest <- t.test(use_data_ctrp$Pearson_GE_Abs ~ use_data_ctrp$InG2P)
    ctrp_ge_res <- paste0("t(", trunc(ctrp_ge_ttest$parameter), ") = ", round(ctrp_ge_ttest$statistic, 2), ", p = ", round(ctrp_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_ctrp_cn_summ) <= 1) {
    ctrp_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn < 2) {
    ctrp_cn_res <-  NA
  }
  else if(use_data_ctrp_cn_summ[use_data_ctrp_cn_summ$InG2P == "Yes",]$nn >= 2) {
    ctrp_cn_ttest <- t.test(use_data_ctrp$Pearson_CN_Abs ~ use_data_ctrp$InG2P)
    ctrp_cn_res <- paste0("t(", trunc(ctrp_cn_ttest$parameter), ") = ", round(ctrp_cn_ttest$statistic, 2), ", p = ", round(ctrp_cn_ttest$p.value, 3))
  }
  print("CTRP testing: DONE")

  use_data_gdsc <- filter(use_data, Dataset == "GDSC")
  use_data_gdsc_ge_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_GE_Abs),] %>% count(InG2P)
  use_data_gdsc_cn_summ <- use_data_gdsc[!is.na(use_data_gdsc$Pearson_CN_Abs),] %>% count(InG2P)
  gdsc_ge_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  gdsc_cn_ttest <- data.frame(statistic = NA, parameter = NA, p.value = NA)
  if(nrow(use_data_gdsc_ge_summ) <= 1) {
    gdsc_ge_res <-  NA
    ticker_ge <- ticker_ge + 1
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_ge_res <-  NA
  }
  else if(use_data_gdsc_ge_summ[use_data_gdsc_ge_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_ge_ttest <- t.test(use_data_gdsc$Pearson_GE_Abs ~ use_data_gdsc$InG2P)
    gdsc_ge_res <- paste0("t(", trunc(gdsc_ge_ttest$parameter), ") = ", round(gdsc_ge_ttest$statistic, 2), ", p = ", round(gdsc_ge_ttest$p.value, 3))
  }
  if(nrow(use_data_gdsc_cn_summ) <= 1) {
    gdsc_cn_res <-  NA
    ticker_cn <- ticker_cn + 1
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn < 2) {
    gdsc_cn_res <-  NA
  }
  else if(use_data_gdsc_cn_summ[use_data_gdsc_cn_summ$InG2P == "Yes",]$nn >= 2) {
    gdsc_cn_ttest <- t.test(use_data_gdsc$Pearson_CN_Abs ~ use_data_gdsc$InG2P)
    gdsc_cn_res <- paste0("t(", trunc(gdsc_cn_ttest$parameter), ") = ", round(gdsc_cn_ttest$statistic, 2), ", p = ", round(gdsc_cn_ttest$p.value, 3))
  }
  print("GDSC testing: DONE")

  y_value_ge <- ifelse(ticker_ge == 3, 10, max(use_data$n) + 1)
  y_value_cn <- ifelse(ticker_cn == 3, 10, max(use_data$n) + 1)
  summ_text <- data.frame(Dataset = c("CCLE", "CTRP", "GDSC"),
                          Test_Results_GE = c(ccle_ge_res, ctrp_ge_res, gdsc_ge_res),
                          t_statistic_GE = c(round(ccle_ge_ttest$statistic, 3), round(ctrp_ge_ttest$statistic, 3), round(gdsc_ge_ttest$statistic, 3)),
                          df_GE = c(trunc(ccle_ge_ttest$parameter), trunc(ctrp_ge_ttest$parameter), trunc(gdsc_ge_ttest$parameter)),
                          p_value_GE = c(round(ccle_ge_ttest$p.value, 3), round(ctrp_ge_ttest$p.value, 3), round(gdsc_ge_ttest$p.value, 3)),
                          Test_Results_CN = c(ccle_cn_res, ctrp_cn_res, gdsc_cn_res),
                          t_statistic_CN = c(round(ccle_cn_ttest$statistic, 3), round(ctrp_cn_ttest$statistic, 3), round(gdsc_cn_ttest$statistic, 3)),
                          df_CN = c(trunc(ccle_cn_ttest$parameter), trunc(ctrp_cn_ttest$parameter), trunc(gdsc_cn_ttest$parameter)),
                          p_value_CN = c(round(ccle_cn_ttest$p.value, 3), round(ctrp_cn_ttest$p.value, 3), round(gdsc_cn_ttest$p.value, 3)),
                          group_general_lineage_name = lineage)

@@

```{r}
g2p <- read.delim("./data_munging/g2p_full_level_A_dataset_NEW_DEC_2_2018_withGroupedLineages.csv", sep = "\t", header = TRUE)
g2p[, 1:2] <- NULL
g2p <- merge(g2p, lineage_converter, by = "grouped_general_doid", all.x = TRUE)

@@

```{r}
crispr_signif_g2p_gene <- readRDS("./data_munging/rds/crispr_signif_g2p_gene.rds")
crispr_signif_g2p_gene <- rbind(crispr_signif_g2p_gene, c("G6PD", rep(NA, 11)))
knitr::kable(crispr_signif_g2p_gene[, c("Hugo_Symbol", "p", "p.adj", "p.format", "p.signif", "p.signif.adj")], caption = "Wilcoxon test results for Level A point mutations (* p <= 0.05, ** p <= 0.01, *** p <= 0.001, **** p <= 0.0001)") %>% kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>% scroll_box(width = "900px", height = "450px")
```

@@

#### CRISPR

```{r fig.height=1.5, fig.width=12}
crispr_signif_g2p_gene$y_label <- "CRISPR"
crispr_signif_g2p_gene$Hugo_Symbol <- factor(crispr_signif_g2p_gene$Hugo_Symbol, levels = g2p_genes)
crispr_signif_g2p_gene$p <- as.numeric(as.character(crispr_signif_g2p_gene$p))

crispr_mut_heatmap_plot <- ggplot(data = crispr_signif_g2p_gene, aes(x = Hugo_Symbol, y = y_label)) +
  geom_tile(aes(fill = p)) +
  scale_fill_gradientn(colors = c("darkgreen", "white", "white"), values = c(0, 0.05, 1), na.value = "darksalmon") +
  scale_x_discrete(drop = FALSE) +
  theme(axis.title.y = element_blank(), axis.text.x = element_text(angle = 90, hjust = 1, vjust = 0.4, size = 10)) +
  labs(x = "Gene")

# write.table(crispr_signif_g2p_gene, file = "~/Desktop/crispr_signif_g2p_gene_20181203.csv", quote = FALSE, sep = ",", row.names = FALSE)
# ggsave("./plots/manuscript/crispr_mut_heatmap_plot_example.png", crispr_mut_heatmap_plot, device = "png", dpi = 450, width = 12, height = 1.5, units = "in")
```

@@

gdsc_druggene_summ <- merge(g2p_druggene_p_tally, gdsc_signif_g2p_grid[, c("Drug_Gene", "p")], by = "Drug_Gene", all = TRUE)
gdsc_druggene_summ$n <- ifelse(is.na(gdsc_druggene_summ$n), 0, gdsc_druggene_summ$n)
gdsc_druggene_summ$InG2P <- ifelse(gdsc_druggene_summ$n != 0, "Yes", "No")
gdsc_druggene_summ$Dataset <- "GDSC"
gdsc_p_ttest <- t.test(gdsc_druggene_summ$p ~ gdsc_druggene_summ$InG2P)
gdsc_p_ttest_res <- paste0("t(", round(gdsc_p_ttest$parameter, 0), ") = ", round(gdsc_p_ttest$statistic, 2), ", p = ", formatC(gdsc_p_ttest$p.value, digits = 2, format = "f"))

@@

ggsave("./plots/manuscript/g2p_druggene_mut_plot.png", g2p_druggene_mut_plot, device = "png", dpi = 450, width = 12, height = 5, units = "in")
```

@@

# ggsave("./plots/manuscript/g2p_druggene_cn_plot.png", g2p_druggene_cn_plot, device = "png", dpi = 450, width = 12, height = 5.5, units = "in")
```

@@

Mutation status summary stats:
```{r}
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ
g2p_druggene_all_summ_stats$n_true <- TRUE
g2p_druggene_all_summ_stats <- g2p_druggene_all_summ_stats %>% drop_na(p) %>% group_by(Dataset, InG2P) %>% summarize(p_mean = round(mean(p), 2), p_sd = round(sd(p), 2), n = sum(n_true), n_signif = sum(p < 0.05), n_sig_perc = n_signif / n * 100)
```

Pearson summary stats:
```{r fig.height=4, fig.width=5}
g2p_druggene_pearson_stats <- g2p_druggene_pearson
g2p_druggene_pearson_stats$n_true <- TRUE
g2p_druggene_pearson_stats <- g2p_druggene_pearson_stats %>% group_by(Dataset, InG2P) %>% drop_na() %>% summarize(
          ge_mean = round(mean(Pearson_GE_Abs), 5),
          ge_sd = round(sd(Pearson_GE_Abs), 5),
          ge_n = sum(n_true),
          ge_n_signif = sum(Pearson_Pval_GE < 0.05),
          ge_n_sig_perc = ge_n_signif / ge_n * 100,
          cn_mean = round(mean(Pearson_CN_Abs), 3),
          cn_sd = round(sd(Pearson_CN_Abs), 5),
          cn_n = sum(n_true),
          cn_n_signif = sum(Pearson_Pval_CN < 0.05),
          cn_n_sig_perc = cn_n_signif / cn_n * 100)
